Exact Phylodynamic Likelihood\\ via Structured Markov Genealogy Processes

### 2024-05-28 ms.Rnw
more specificity on software versions

<<prefix,include=FALSE,cache=FALSE,purl=FALSE>>=
prefix <- "sgp"
source("setup.R")
@
<<packages,include=FALSE,cache=FALSE>>=
library(tidyverse)
library(ggtree)
library(pomp)
library(cowplot)
library(viridis)
library(phylopomp)
stopifnot(getRversion() >= "4.3")
stopifnot(packageVersion("pomp")>="5.8")
stopifnot(packageVersion("phylopomp")>="0.12.0.1")
theme_set(theme_bw(base_family="serif"))
options(
  width=150,
  keep.source=TRUE,
  encoding="UTF-8",
  stringsAsFactors=FALSE,
  dplyr.summarise.inform=FALSE,
  pomp_archive_dir="results"
)
set.seed(1159254136)
@

>>>>

<<prefix,include=FALSE,cache=FALSE,purl=FALSE>>=
prefix <- "sgp"
source("setup.R")
@
<<packages,include=FALSE,cache=FALSE>>=
library(tidyverse)
library(ggtree)
library(pomp)
library(cowplot)
library(viridis)
library(phylopomp)
stopifnot(getRversion() >= "4.3")
stopifnot(packageVersion("pomp")>="5.8.4")
stopifnot(packageVersion("phylopomp")=="0.12.0.1")
theme_set(theme_bw(base_family="serif"))
options(
  width=150,
  keep.source=TRUE,
  encoding="UTF-8",
  stringsAsFactors=FALSE,
  dplyr.summarise.inform=FALSE,
  pomp_archive_dir="results"
)
set.seed(1159254136)
@
